\documentclass[10pt, a4paper]{article}
\usepackage[
a4paper,
total={6.3in, 9.85in},
bmargin=0.5in
 ]{geometry}
\usepackage{enumitem}% http://ctan.org/pkg/enumitem
\usepackage[utf8]{inputenc}
\usepackage{eso-pic} % \AddToShipoutPicture
\usepackage{fontspec}
\usepackage{pgfplots}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{mdframed}
\usepackage{float}
\usepackage{amsmath}
\usepackage{flafter}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{blindtext}
\usepackage{pgfplots}
\usepackage{seqsplit}
\usepackage[cache=false]{minted}
\usepackage{stmaryrd}
\usepackage{semantic}
\usepackage{url}
\usepackage{color}
\usepackage{flushend}
\usepackage{subfigure}
\usepackage{tikz}
\usepackage{svg}
\usepackage{pdfpages}
\usepackage{titling}
\usepackage{titlesec}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 0pt}
\titlespacing\subsection{0pt}{6pt plus 4pt minus 2pt}{0pt plus 2pt minus 0pt}

\usepackage{cleveref}
\usepackage[parfill]{parskip}
\usepackage[toc,page]{appendix}
\setmainfont{Latin Modern Sans}

\usepackage{tcolorbox}
\usepackage{etoolbox}

% pdffor adjustwidth environment
\usepackage[strict]{changepage}

\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
\lhead{Curriculum Vitae for Mikkel Storgaard Knudsen}

\begin{document}
Mikkel Storgaard Knudsen \\
Bogtrykkervej 16 2.tv \\
2400 København NV \\
42 43 41 45 \\
mikkelstorgaard@gmail.com

\subsection*{Summary}
I am a Master's graduate in Computer Science from the University of Copenhagen,
and am currently working full-time as a software developer in Copenhagen.

In the last several years, I have increasingly been getting involved in complex
projects in fields, I haven't necessarily worked with before. In particular, I thrive with tasks related to
research, development and problem solving, and I make an effort of delivering
tangible and quantifiable results.\\
My practical experience shows this by having a 100\% implementation rate of products
from both student jobs and academic projects, always backing up my results with
data and benchmarks.

As a person I am outgoing and sociable, and I enjoy contributing to my
workplace professionally as well as socially, in example by arranging after-hours social
events.

I am looking forward to becoming part of a talented team of highly capable
colleagues in a high skill ceiling environment, where I can partake in solving high
complexity tasks, as well as hone myself professionally by learning from the
best.

\subsection*{Professional experience}
\textbf{Software developer at Abacus Medicine} \textit{(August 2019 --)}
  \begin{itemize}[topsep=0pt]
  \item Main feature developer on internal proprietary \textit{assisted
      decision-making} trading platform.

  \item Primary tasks include front- and backend design, testing and
    implementation, in addition to DevOps tasks such as the ongoing tweaking
    of our continuous integration and -deployment pipeline.

  \item Key part of weekly meetings with internal stakeholders and developers, collaborating
    on resolving design problems, prioritizing new features, and roadmapping. 
  \end{itemize}

  At Abacus Medicine, I primarily work with OCaml, C\#, Microsoft's T-SQL and
  Docker, together with Azure, Jira and Bitbucket.

\textbf{Backend developer at June by Danske Bank} \textit{(March 2017 -- February 2019)}
  \begin{itemize}[topsep=0pt]
  \item Primary responsible the current design and
  implementation of our image recognition engine, which is used for
  verifying customer identity documents during our customer onboarding
  \textit{KYC}\footnote{Know Your Customer; in other words the step of verifying a
    customer's identity.} process, increasing from 56\% to \textasciitilde 92\%.

  \item Responsibility for developing a document rendering
  engine in use for generating contracts and other legal documents
  during customer onboarding and fund transactions.

  \item Development of tools for our Quality Assurance division. 

  \item Part of the feature development team in June, with responsibilities in 
  software implementation, code reviews, sprint planning and
  ticket grooming sessions.
  \end{itemize}

  At June, my primary tools have been C\#, Python, OpenCV, Tesseract OCR, LaTeX, Docker, Elm and Node.js

\textbf{Full-stack Consultant at Eksponent} \textit{(March 2016 -- March 2017)}
\begin{itemize}[topsep=0pt]
\item 
Design-, development- and
deployment responsibilities for client projects, as well as tool development for
internal usage.
\end{itemize}
At Eksponent, my primary tools have been C\#, Umbraco, MSSQL, Azure, Continous
Integration using Travis, and Octopus.\\
  \pagebreak

\textbf{Teaching Assistant at The University of Copenhagen} \textit{(September 2017 -- November 2017)}
\begin{itemize}[topsep=0pt]
\item 
  Teaching assistant on the \textit{Advanced Programming} master's course, where
  I have had the responsibility for preparing and hosting weekly lab sessions
  for my assigned class of students, in addition to correcting, grading and
  giving feedback on weekly assignments.
\item
  The role included grading of the final \textit{Advanced Programming}
  exam submissions.
\end{itemize}

  In \textit{Advanced Programming}, I taught the languages Haskell, Prolog and
  Erlang.

\subsection*{Education}
\textbf{MSc in Computer Science at The University of Copenhagen} \textit{(August 2016 -- January 2019)}\\
  During my master's program, I have focused on courses covering compilers,
  logic, semantics and type theory, and functional and parallel programming,
  including GPGPU\footnote{General Purpose Graphics Processing Unit} programming.

  Among other things, my final year at \textit{UCPH} assisting a Physics Ph.D. student in
  rewriting and refactoring a complex simulation
  from sequential C++, into an elegant and parallel GPU-powered C++/CUDA solution.
  
  For my thesis \textit{FShark: Futhark programming in
    FSharp}\footnote{\url{https://futhark-lang.org/student-projects/mikkel-msc-thesis.pdf}},
  my two biggest contributions was the design and implementation of a C\# backend for
  the Futhark compiler, and the design and implementation of an F\#-to-Futhark transpiler.
  The C\# backend has since become part of the official Futhark compiler, and is
  now enabling developers to effortlessly integrate high-performance GPU-powered
  computational kernels in standard .NET projects.

  My thesis was given the grade \textit{12} at the defense, corresponding to
  an A on the international ECTS scale.
  
\textbf{BSc in Computer Science at The University of Copenhagen} \textit{(August 2012 -- June 2016)}\\
  For my finishing bachelor's project, I extended the Futhark language with type
  aliases, and described a complete design for implementing ML-style higher-order modules.

\textbf{General Certificate of Secondary Education (STX) at Viborg Gymnasium \& HF} \textit{(Finished 2010)}\\
  With a focus on social sciences, English and mathematics.

\subsection*{Skill summary}
Here follows a summary of the languages and technologies that I am experienced in,
and can confidently work with:\\
APL, Bash/Linux, Assembly, C, C++, C\#, CUDA, Elm, Elixir, F\#, Go, Haskell,
Java, JavaScript, Matlab, Node.js, Numpy, OCaml, OpenCL, OpenCV, Python (2 \& 3),
Standard ML, SQL and Tesseract OCR.

Amazon Web Services, Azure, Benchmarking, DSL design and -implementation, Docker, functional
programming, Git, GPGPU programming, Jenkins, Octopus, SCRUM/agile development,
Test-Driven Development, Travis, parallel programming, property-based testing og
project management using Jira.

I am a competent English speaker and -writer, and am used to work in an
international environment.

\subsection*{About me}
I have been a political activist since 2009, working with both student-, LGBTQ-
and national politics, and I am currently a member and the treasurer of
Enhedslistens Queer Committee.

My spare time is spent on my friends and hobbies: I have large interest in music,
and I play guitar and bass at the amateur level.
In general, I love using the city and it's nightlife, and I am an avid concert- and
cinema-goer. I have spent my time on student revues for the last five years, primarily as a writer
and director, but also on-stage as a singer/actor.

Finally, I also enjoy cycling, video games and cooking.
\end{document}


%%% Local Variables:
%%% coding: utf-8
%%% TeX-command-extra-options: "-shell-escape"
%%% mode: latex
%%% TeX-engine: xetex
%%% End:
